Stochastic Wind Power Forecasting

### 2020-02-07 LaTeX_code/paper/paper_1line.tex
Minor edits

\author[1]{Waled Alhaddad}
\author[2]{Ahmed Kebaier}
\author[3]{ Ra\'ul  Tempone}
%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
\affil[1,3]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
\affil[3]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}
\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}

@@

\begin{figure}
  \includegraphics[width=120mm,scale=1]{plots/1.png}
  \caption{Installed wind and solar power over the years. We recall the importance of accurate forecasts to use green energies optimally. {\color{red} We still have to ensure that the source is trusthable (Renzo will do it)}.}
\end{figure}Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
\item Operation scheduling of controlable power plants.
\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals from the company ADME.}
  \label{fig:sample_data}
\end{figure}

>>>>

%\author[1]{Waled Alhaddad}
\author[1]{Renzo Caballero}
\author[2]{Ahmed Kebaier}
\author[3]{Marco Scavino}
\author[4]{ Ra\'ul  Tempone}
%\author[2]{Corresponding Author\thanks{email@2nduniversity.com}}
\affil[1,4]{CEMSE Division, King Abdullah University of Science and Technology (KAUST), Saudi Arabia}
\affil[2]{Université Paris 13, Sorbonne Paris Cité, LAGA, CNRS (UMR 7539), Villetaneuse, France}
\affil[3]{Universidad de la Rep\'ublica, Montevideo Uruguay}
\affil[4]{Alexander von Humboldt Professor, RWTH Aachen University, Germany}

@@

\begin{figure}
  \includegraphics[width=120mm,scale=1]{plots/1.png}
  \caption{Installed wind and solar power over the years. We recall the importance of accurate forecasts to use green energies optimally. {\color{red} We still have to ensure that the source is trustworthy (Renzo will do it)}. Redo the figure as well}
\end{figure}Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
\item Operation scheduling of controlable power plants.
\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals from  ADME.}
  \label{fig:sample_data}
\end{figure}
